The importance of colormaps

### 2020-06-30 Thyng2020/paper.tex

Plots were created using the following Python packages: matplotlib, Jupyter, numpy, xarray, pandas, cartopy, and colorspacious along with the colormaps packages cmocean, colorcet, and palettable.

>>>>

Plots were created using the following Python packages: Matplotlib, Jupyter, numpy, xarray, pandas, cartopy, and colorspacious along with the colormaps packages cmocean, colorcet, and palettable.
